Complex Quasiperiodic Variables from Four Years of TESS

### 2023-06-13 paper/ms.tex
update ms

For the TESS sectors in which these objects were identified, they show
anywhere from one to eight local minima per cycle.
Some stars show relatively ordinary modulation during one continuous
portion of the phased light curve, and highly structured modulation in
the remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
TIC~402980664).
Others show structured modulation over the entire span of a cycle
(e.g. TIC~2234692, TIC~401789285, TIC~425933644, TIC~142173958).
Others still show some mix between these two modes,
with one or more small dips, superposed over one or more large dips.
Frankly, staring at them for long enough,
it becomes possible to identify any one of them

@@

\begin{figure*}[!t]
	\begin{center}
			\centering
			\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_changers.pdf}
		\vspace{-0.2cm}
		\caption{
		{\bf Evolution of CQVs}: ``Before and
      after'' for six CQVs from Figure~\ref{fig:revolution}.  Panels
      in the top two rows are separated by two years
      ($\approx$$10^3$ cycles); each panel shows one month.
      Periods are listed in hours. 
      {\bf todo: make these for everything.}
%			\vspace{-0.8cm}
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5604_2min_phase_timegroups_mosaic.pdf}
		\vspace{-0.45cm}
		\caption{
			{\it Bottom:}
      Evolution of LP 12-502 ($P$=18.6\,h) at fixed period over three
      years; small text denotes cycle number.  The TESS pointing law
      dictates time gaps; larger gaps tend to yield larger shape
      changes.
      The dips usually evolve over tens to hundreds of cycles.
      However cycles 1233-1264 show a dip that ``switched'' from a depth
      and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
      one cycle.
			\vspace{-0.8cm}
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{402980664_S0018_120sec_cpvvetter.pdf}
		\vspace{-0.45cm}
		\caption{
      Validation plots used to label CQVs (the complete figure
      set of \ncpvsfound\ images is available online).
      Panels are as follows.
      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
      data and black points are binned to 200 points per cycle.
      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
      Dotted lines show up to the 10$^{\rm th}$ harmonic and
      subharmonic.
      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
      circles displayed for scale.
      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
      Barycentric TESS Julian Date (BTJD).
      {\it e)}: Phase-folded light curve, binned to 100 points per
      cycle.  The gray line denotes the automated spline-fit to the
      wrapped phase-folded light curve, and small gray triangles
      denote automatically identified local minima.
      {\it f)}: Phase-folded light curve at twice the peak period.
      {\it g)}: Phase-folded light curve at half the peak period.
      {\it h)}: Phase-folded time-series within the ``background''
      aperture defined in the SPOC light curves.
      {\it i)}: Phase-folded flux-weighted centroid in the column
      direction.
      {\it j)}: Phase-folded flux-weighted centroid in the row
      direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN-$\Sigma$ v1.1 association probabilities, calculated
      using positions, proper motions, and the parallax.
      }
		\label{fig:vet}
	\end{center}
\end{figure*}

>>>>

For the TESS sectors in which these objects were identified, they show
anywhere from one to eight local minima per cycle.
Some stars show relatively ordinary modulation during one continuous
portion of the phased light curve, and highly structured modulation in
the remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
TIC~402980664).
Others show structured modulation over the entire span of a cycle
(e.g. TIC~2234692, TIC~401789285, TIC~425933644, TIC~142173958).
Others still show some mix between these two modes,
with one or more small dips, superposed over one or more large dips.

@@

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5604_2min_phase_timegroups_mosaic.pdf}
		\vspace{-0.45cm}
		\caption{
			{\it Bottom:}
      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period over three
      years; small text denotes cycle number.  The TESS pointing law
      dictates time gaps; larger gaps tend to yield larger shape
      changes.
      The dips usually evolve over tens to hundreds of cycles.
      However cycles 1233-1264 show a dip that ``switched'' from a depth
      and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
      one cycle.
			\vspace{-0.8cm}
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_allchangers_2count_showtitles.png}
		\vspace{-0.2cm}
		\caption{
			{\bf Evolution of CQVs}: ``Before and
			after'...  Panels
			in the top two rows are separated by two years
			($\approx$$10^3$ cycles); each panel shows one month.
			Periods are listed in hours. 
			{\bf todo: fix the plot and the caption.}
			%			\vspace{-0.8cm}
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=0.96\textwidth]{402980664_S0018_120sec_cpvvetter.pdf}
		\vspace{-0.45cm}
		\caption{
      Validation plots used to label CQVs (the complete figure
      set of \ncpvsfound\ images is available online).
      Panels are as follows.
      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
      data and black points are binned to 200 points per cycle.
      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
      Dotted lines show up to the 10$^{\rm th}$ harmonic and
      subharmonic.
      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
      circles displayed for scale.
      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
      Barycentric TESS Julian Date (BTJD).
      {\it e)}: Phase-folded light curve, binned to 100 points per
      cycle.  The gray line denotes the automated spline-fit to the
      wrapped phase-folded light curve, and small gray triangles
      denote automatically identified local minima.
      {\it f)}: Phase-folded light curve at twice the peak period.
      {\it g)}: Phase-folded light curve at half the peak period.
      {\it h)}: Phase-folded time-series within the ``background''
      aperture defined in the SPOC light curves.
      {\it i)}: Phase-folded flux-weighted centroid in the column
      direction.
      {\it j)}: Phase-folded flux-weighted centroid in the row
      direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN-$\Sigma$ v1.1 association probabilities, calculated
      using positions, proper motions, and the parallax.
      }
		\label{fig:vet}
	\end{center}
\end{figure*}
